\documentclass[10pt]{article}

\usepackage[letterpaper,margin=0.65in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{url}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

\hypersetup{
  colorlinks=true,
  urlcolor=blue!55!black,
  linkcolor=blue!55!black
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\raggedright
\setlist[itemize]{leftmargin=1.2em,itemsep=1pt,topsep=2pt,parsep=0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{5pt}

\newcommand{\entry}[4]{%
  \textbf{#1} \hfill \emph{#2}\\
  #3 \hfill #4\\[-2pt]
}

\newcommand{\ccf}[1]{\textcolor{red}{(CCF-#1)}}

\newcommand{\pub}[4]{%
  \item \textit{#1}.\\
  #2\\
  #3 #4
}

\begin{document}

\begin{center}
  {\LARGE \textbf{Jingbang Chen}}\\
  Research Assistant Professor, School of Data Science, The Chinese University of Hong Kong, Shenzhen\\
  Research Assistant Professor, Shenzhen Loop Area Institute (SLAI)\\
  \href{mailto:chenjb@cuhk.edu.cn}{chenjb@cuhk.edu.cn}
  \quad|\quad +86 13922158991
  \quad|\quad \url{https://chenjb1997.github.io}
\end{center}

\section*{Research Interests}
Design, analysis, and implementation of provably efficient graph algorithms and data structures, with extensions on large-scale data management, data mining, machine learning and artificial intelligence.

\section*{Career}
\entry{Research Assistant Professor}{Sep 2025 -- present}
{School of Data Science, The Chinese University of Hong Kong, Shenzhen}{Shenzhen, China}
\entry{Research Assistant Professor}{Sep 2025 -- present}
{Shenzhen Loop Area Institute (SLAI)}{Shenzhen, China}
\textbf{Co-founder and Co-president} \hfill \emph{2022 -- present}\\
Universal Cup, \url{https://ucup.ac/}\\[-2pt]
\begin{itemize}
  \item Co-founded and co-lead a non-profit organization serving the global competitive programming community.
  \item Provide high-quality training resources and host onsite global events for top competitive programmers.
  \item Build communication bridges across industry, academia, and the competitive programming community.
  \item Supported participation from over 8,000 teams from more than 500 affiliations worldwide.
  \item Hosted the 2024 Universal Cup Summer Summit in Cancun and the 2025 and 2026 Universal Cup Finals in Dongguan and Shanghai.
\end{itemize}

\section*{Education}
\entry{University of Waterloo}{2023 -- 2025}
{Ph.D. in Computer Science, Algorithms \& Complexity Group}{Waterloo, Canada}
Advisor: Richard Peng

\entry{Georgia Institute of Technology}{2020 -- 2022}
{M.S. in Computer Science}{Atlanta, USA}
Advisor: Richard Peng

\entry{Zhejiang University}{2016 -- 2020}
{B.Eng. (Honors), Pursuit Science Class in Computer Science, Chu Kochen Honors College}{Hangzhou, China}
Advisor: Can Wang

\section*{Students}
\textbf{CUHK-Shenzhen}
\begin{itemize}
  \item \textbf{Tianran Zhu}, Ph.D., Fall 2026 -- current. B.S. Peking University; ICPC Gold; NOI Silver.
  \item \textbf{Junyang Chen}, M.Phil., Fall 2026 -- current. B.S. South China Normal University.
  \item \textbf{Jiajun Hou}, M.Phil., Fall 2026 -- current. B.S. Beijing Normal-Hong Kong Baptist University.
  \item \textbf{Zixuan Yu}, M.Phil., Fall 2026 -- current. B.S. Sun Yat-sen University.
  \item \textbf{Yichun Wang}, M.Phil., Fall 2026 -- current. B.S. CUHK-Shenzhen.
\end{itemize}

\textbf{CUHK-Shenzhen + SLAI}
\begin{itemize}
  \item \textbf{Yuyang Zhao}, Ph.D., Fall 2025 -- current. B.S. Huaqiao University; ICPC Gold; NOI Silver. Co-advised with Prof. Zhi-Quan (Tom) Luo.
  \item \textbf{Yuanjin Zheng}, Ph.D., Fall 2026 -- current. B.S. Zhejiang University.
  \item \textbf{Minghao Li}, Ph.D., Fall 2026 -- current. B.S. Nankai University; M.S. The University of Hong Kong.
\end{itemize}

\textbf{External Ph.D.}
\begin{itemize}
  \item \textbf{Zeyu Wang}, Zhejiang University, Fall 2025 -- current. Co-advised with Prof. Can Wang.
  \item \textbf{Daniel Skachkov}, Moscow State University, Spring 2026 -- current. Co-advised with Prof. Yuriy Dorn.
\end{itemize}

\textbf{Research Assistants}
\begin{itemize}
  \item \textbf{Hao Wu}, Zhejiang University, Fall 2025 -- current. ICPC Gold.
  \item \textbf{Sichen Wang}, Shenzhen MSU-BIT University, Fall 2025 -- current.
  \item \textbf{Weinuo Li}, Zhejiang University, Fall 2024 -- Spring 2026. B.S. and M.S. Zhejiang University. Now at Yanfu Investments; VLDB 2026; ICPC Gold; ICPC Champion; ICPC WF 10th.
\end{itemize}

\section*{Teaching}
\begin{itemize}
  \item CSC 5001, Design and Analysis of Computer Algorithms, CUHK-Shenzhen, Fall 2025.
  \item CSC 5003, Algorithm Art and Programming Practice, CUHK-Shenzhen, Spring 2026 and Spring 2027.
  \item CSC 3200, Data Structures and Advanced Programming, CUHK-Shenzhen, Fall 2026.
  \item MF 0005, Analysis of Algorithms, SLAI, Spring 2026. Co-teaching with Prof. Konstantinos Courcoubetis.
\end{itemize}

\section*{Publications}
* indicates first author or equal contribution; \textsuperscript{\textdagger} indicates corresponding author.
\begin{enumerate}[leftmargin=1.7em,itemsep=4pt,topsep=3pt]
  \pub{Scalable Approximate Biclique Counting over Large Bipartite Graphs}
  {\textbf{Jingbang Chen}*, Weinuo Li, Yingli Zhou, Hangrui Zhou, Qiuyang Mang, Can Wang, Yixiang Fang, Chenhao Ma.}
  {International Conference on Very Large Data Bases (VLDB 2026) \ccf{A}.}
  { \href{https://arxiv.org/abs/2505.10471}{arXiv}; \href{https://doi.org/10.14778/3785297.3785301}{DOI}}

  \pub{On the Power of Learning-Augmented Search Trees}
  {\textbf{Jingbang Chen}*, Xinyuan Cao, Alicia Stepin, Li Chen.}
  {International Conference on Machine Learning (ICML 2025) \ccf{A}.}
  { \href{https://arxiv.org/abs/2211.09251}{arXiv}; \href{https://proceedings.mlr.press/v267/chen25e.html}{Proceedings}}

  \pub{Scalable Algorithm for Finding Balanced Subgraphs with Tolerance in Signed Networks}
  {\textbf{Jingbang Chen}*, Qiuyang Mang, Hangrui Zhou, Richard Peng, Yu Gao, Chenhao Ma.}
  {ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD 2024) \ccf{A}.}
  { \href{https://arxiv.org/abs/2402.05006}{arXiv}; \href{https://doi.org/10.1145/3637528.3671674}{DOI}}

  \pub{Efficient Historical Butterfly Counting in Large Temporal Bipartite Networks via Graph Structure-aware Index}
  {Qiuyang Mang, \textbf{Jingbang Chen}*, Hangrui Zhou, Yu Gao, Yingli Zhou, Qingyu Shi, Richard Peng, Yixiang Fang, Chenhao Ma.}
  {International Conference on Very Large Data Bases (VLDB 2025) \ccf{A}.}
  { \href{https://arxiv.org/abs/2406.00344}{arXiv}; \href{https://doi.org/10.14778/3725688.3725693}{DOI}}

  \pub{Curing ``Miracle Steps'' in LLM Math Reasoning with Rubric Rewards}
  {Youliang Yuan, Qiuyang Mang, \textbf{Jingbang Chen}, Hong Wan, Xiaoyuan Liu, Junjielong Xu, Jen-tse Huang, Wenxuan Wang, Wenxiang Jiao, Pinjia He.}
  {Annual Meeting of the Association for Computational Linguistics, Main Conference (ACL 2026) \ccf{A}.}
  { \href{https://arxiv.org/abs/2510.07774}{arXiv}}

  \pub{FrontierCS: Evolving Challenges for Evolving Intelligence}
  {Qiuyang Mang et al., including \textbf{Jingbang Chen}, Aleksandra Korolova, Peter Henderson, Pramod Viswanath, Vijay Ganesh, Saining Xie, Zhuang Liu, Dawn Song, Sewon Min, Ion Stoica, Joseph E. Gonzalez, Jingbo Shang, Alvin Cheung.}
  {International Conference on Machine Learning (ICML 2026) \ccf{A}.}
  { \href{https://arxiv.org/abs/2512.15699}{arXiv}}

  \pub{BEAR: Towards Beam-Search-Aware Optimization for Recommendation with Large Language Models}
  {Weiqin Yang, Bohao Wang, Zhenxiang Xu, Jiawei Chen, Shengjia Zhang, \textbf{Jingbang Chen}, Canghong Jin, Can Wang.}
  {International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR 2026) \ccf{A}.}
  { \href{https://arxiv.org/abs/2601.22925}{arXiv}}

  \pub{TopKGAT: A Top-K Objective-Driven Architecture for Recommendation}
  {Sirui Chen, Jiawei Chen, Canghong Jin, Sheng Zhou, \textbf{Jingbang Chen}, Wujie Sun, Can Wang.}
  {The Web Conference (WWW 2026) \ccf{A}.}
  { \href{https://arxiv.org/abs/2601.18432}{arXiv}; \href{https://doi.org/10.1145/3774904.3792717}{DOI}}

  \pub{Distance Queries over Dynamic Interval Graphs}
  {\textbf{Jingbang Chen}*, Meng He, J. Ian Munro, Richard Peng, Kaiyu Wu, Daniel J. Zhang.}
  {International Symposium on Algorithms and Computation (ISAAC 2023) \ccf{C}; Computational Geometry: Theory and Applications, Volume 122 \ccf{C}.}
  { \href{https://doi.org/10.4230/LIPIcs.ISAAC.2023.18}{DOI}; \href{https://doi.org/10.1016/j.comgeo.2024.102103}{Journal DOI}}

  \pub{Exponential Convergence of Sinkhorn Under Regularization Scheduling}
  {\textbf{Jingbang Chen}*, Li Chen, Yang P. Liu, Richard Peng, Arvind Ramaswami.}
  {SIAM Conference on Applied and Computational Discrete Algorithms (ACDA 2023).}
  { \href{https://arxiv.org/abs/2207.00736}{arXiv}; \href{https://doi.org/10.1137/1.9781611977714.16}{DOI}}

  \pub{Hardness of Graph-Structured Algebraic and Symbolic Problems}
  {\textbf{Jingbang Chen}*, Yu Gao, Yufan Huang, Richard Peng, Runze Wang.}
  {Algorithms and Data Structures Symposium (WADS 2023).}
  { \href{https://arxiv.org/abs/2109.12736}{arXiv}}

  \pub{Fast Adaptively Weighted Matrix Factorization for Recommendation with Implicit Feedback}
  {Jiawei Chen, Can Wang, Sheng Zhou, Qihao Shi, \textbf{Jingbang Chen}, Yan Feng, Chun Chen.}
  {AAAI Conference on Artificial Intelligence (AAAI 2020) \ccf{A}.}
  { \href{https://arxiv.org/abs/2003.01892}{arXiv}; \href{https://ojs.aaai.org/index.php/AAAI/article/view/5751}{Proceedings}}
\end{enumerate}

\section*{Manuscripts}
\begin{enumerate}[leftmargin=1.7em,itemsep=4pt,topsep=3pt]
  \pub{Scalable Algorithm for Dynamic Quasi-clique Detection}
  {\textbf{Jingbang Chen}*, Weinuo Li, Yingli Zhou, Hao Wu, Can Wang, Yixiang Fang, Chenhao Ma.}
  {Manuscript, 2026.}
  { \href{https://arxiv.org/abs/2605.26235}{arXiv}}

  \pub{Finding the Balance Rate of Uncertain Signed Graphs}
  {Zeyu Wang, Kudria Sergei, \textbf{Jingbang Chen}\textsuperscript{\textdagger}, Jiawei Chen, Xinyu Wang, Xiaodong Luo, Can Wang.}
  {Manuscript, 2026.}
  { \href{https://arxiv.org/abs/2605.17492}{arXiv}}

  \pub{Nearly Optimal Internal Dictionary Matching}
  {\textbf{Jingbang Chen}*, Jiangqi Dai, Qiuyang Mang, Qingyu Shi, Tingqiang Xu.}
  {Manuscript, 2024.}
  { \href{https://arxiv.org/abs/2312.11873}{arXiv}}

  \pub{Sandpile Prediction on Undirected Graphs}
  {Ruinian Chang, \textbf{Jingbang Chen}*, J. Ian Munro, Richard Peng, Qingyu Shi, Zeyu Zheng.}
  {Manuscript, 2023.}
  { \href{https://arxiv.org/abs/2307.07711}{arXiv}}
\end{enumerate}

\section*{Competitive Programming}
\textbf{Selected results as contestant}
\begin{itemize}
  \item International Grandmaster on Codeforces, max rating 2735.
  \item Champion, ICPC Asia Qingdao Regional, 2017; Champion, ICPC Southeast USA Regional, 2021.
  \item 3rd Place, ICPC North America Championship, 2021; 13th Place, 46th ICPC World Finals, 2024; 56th Place, 42nd ICPC World Finals, 2018.
  \item 12 gold medals in ICPC/CCPC series contests; Bronze Medal, National Olympiad in Informatics (NOI), 2015.
\end{itemize}

\textbf{Coaching, judging, and community}
\begin{itemize}
  \item Coach and deputy leader, Egyptian Olympiad in Informatics (EOI), 2023 -- present.
  \item Trainer, North American Programming Camp (NAPC), 2024 -- present.
  \item Coach, Georgia Tech Programming Team, 2021 -- 2023; Student co-coach, Zhejiang University Competitive Programming Team, 2018 -- 2021.
  \item Contest director and chief judge, ICPC National Invitational Contest (Shenzhen), the first ICPC event hosted at CUHK-Shenzhen.
  \item Chief judge, ICPC East-Continent Finals, 2025.
  \item Problem setter and judge for ICPC Regionals (Qingdao 2018; Nanjing 2020--2025; Macau 2021--2022; Jinan 2023; Hangzhou 2024), provincial contests, Moscow Pre-Finals Workshop, Petrozavodsk Training Camp, OpenCup, Codeforces Round \#573, and Universal Cup.
\end{itemize}

\section*{Service}
\begin{itemize}
  \item Reviewer for WWW 2026, KDD 2026, ISAAC 2025, FOCS 2025, TKDE 2025, KDD 2025, WWW 2025, SODA 2024, SoCG 2024, ICALP 2024, ESA 2024, ACDA 2023.
  \item Member, SUA Programming Competitions Problems Setter Team.
\end{itemize}

\end{document}
